\documentclass{article}
\usepackage{amsfonts, graphicx, multicol, amssymb, amsmath}
%usepackage{ulem}
\usepackage[left=.4in,top=.4in,right=.4in,nohead,nofoot]{geometry}
\newcommand{\example}{\subsubsection*{Example}}


\newcommand\tr{\textrm{tr}}
\newcommand{\vecxx}[2]{\begin{bmatrix} #1\\ #2\\ \end{bmatrix}}
\newcommand{\vecxxx}[3]{\begin{bmatrix} #1\\ #2\\ #3 \end{bmatrix}}
\newcommand{\vecxxxx}[4]{\begin{bmatrix} #1\\ #2\\ #3\\ #4 \end{bmatrix}}

\newcommand{\svecxx}[2]{\left[\begin{smallmatrix} #1\\ #2\\ \end{smallmatrix}\right]}
\newcommand{\svecxxx}[3]{\left[\begin{smallmatrix} #1\\ #2\\ #3 \end{smallmatrix}\right]}
\newcommand{\svecxxxx}[4]{\left[\begin{smallmatrix} #1\\ #2\\ #3\\ #4 \end{smallmatrix}\right]}

\newcommand\matxx[4]{\begin{bmatrix}#1 & #2\\ #3 & #4\end{bmatrix}}
\newcommand\matxxx[9]{\begin{bmatrix}#1 & #2 & #3\\ #4& #5 & #6\\ #7 & #8 & #9\end{bmatrix}}

\newcommand\diagxx[2]{\begin{bmatrix}#1 & 0\\ 0 & #2\end{bmatrix}}
\newcommand\diagxxx[3]{\begin{bmatrix}#1 & 0 & 0\\ 0& #2 & 0\\ 0 & 0 & #3\end{bmatrix}}
\newcommand\idxx{\begin{bmatrix}1 & 0\\ 0 & 1\end{bmatrix}}
\newcommand\idxxx{\begin{bmatrix}1 & 0 & 0\\ 0 & 1 & 0\\ 0 & 0 & 1\end{bmatrix}}
\newcommand\idxxxx{\begin{bmatrix}1 & 0 & 0 & 0\\ 0 & 1 & 0 & 0\\ 0 & 0 & 1 & 0\\ 0 & 0 & 0 & 1\end{bmatrix}}

\newcommand\bR{\mathbb{R}}
\newcommand\bC{\mathbb{C}}


\begin{document}

%%%%%HEADING
\noindent.\hrulefill.\\
\begin{minipage}{0.5\textwidth}
\noindent \sc{Math 307: Midterm 2}
\end{minipage}
\hfill
\begin{minipage}{0.5\textwidth}
\flushright \sc{Reference: Chapter 1 to 6, Peterson, Sochaki,\\ \emph{Linear Algebra and Differential Equations}.}
\end{minipage}
\begin{minipage}{0.5\textwidth}
\vskip 0.2in
Name:\\
%\noindent ID Number:\\
\end{minipage}
\hfill
\begin{minipage}{0.5\textwidth}
\flushright Score: \hspace{2in}
\end{minipage}
\vskip 0.25in
\hrule

%%%%HEADING
\thispagestyle{empty}
\vskip 0.1in
\begin{center}
\fbox{Note: Notes and calculators are forbidden. Phones must be turned off and closed books.}\\
Show all your work, circle or box your answers. Write sentences and explain your line of thought.
\end{center}
\vskip .15in



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%        Questions       %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{enumerate}
\item \textbf{General Knowledge}
\begin{enumerate}
\item Let $A\in M_n(\mathbb R)$ be a square matrix of size $n$. What is the definition of $A$ being diagonalizable?

\vskip 2.5in

\item Give two criteria which make $A$ diagonalizable.

\vskip 2.5in

\item Is every matrix diagonalizable? If not, give an example of a matrix which is not diagonalizable.
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%        Problems       %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage

\item 
\begin{enumerate}

\item If possible, diagonalize the following matrix.
\[\begin{pmatrix}
-3 & 15 \\
-2 & 8 \\
\end{pmatrix}.\]

\vskip 4in

\item Solve the differential equation:
\[ \left\{ 
\begin{array}{ccc} 
 x' & = & -3x + 15y \\
y'  & = & -2x + 8y \\
\end{array}
\right.
\]
\end{enumerate}

\newpage

\item List all the possible Jordan form of matrices with the following characteristic polynomial. 
\begin{enumerate}
\item $\chi(t) = (t-1)(t-3)^2 $
\item $\chi(t) = (t-2)^3 $
\end{enumerate}

\vskip 3in

\item Let $v$ be the velocity of a mass $m$ falling with initial velocity $v_0= v(0) = 0$ at $t_0=0$. If we take into account the air drag and the acceleration due to gravity, we get that $v$ satisfies the following differential equation \[v' +\frac{\alpha}{m}v =g.\]
Here, $\alpha$ is a constant between $0$ and $1$ which says how strong is the air drag. Solve the differential equation and explain what happens physically.

\newpage 

\item Solve the following nonhomogeneous systems of linear differential equations. 
\begin{enumerate}
\item $y' +3y = \cos (t)$,
\item $y' -2 y = e^{4t} $,
\end{enumerate}

\newpage
\item %%%%%%%%%%%%%%%%%%
Let us start at month $0$ with a couple of rabbits. Each month, a couple of rabbits gives birth to another one, as soon as two months passed since their conception. Let $F_n$ be the number of couple of rabbits after $n$ months, starting with $F_0 = F_1 = 1$. Then 
\[F_{n+2} = F_{n+1}+ F_n,\]
if $n\geq 0$.\\
Let us introduce $X_n = \begin{pmatrix} F_{n+1} \\ F_{n}\end{pmatrix}$. Then:
\[X_{n+1} = A X_n\]
with $A=\begin{pmatrix} 1 & 1 \\ 1 & 0 \end{pmatrix}$. So we get the following relation:
\[X_n = A^n X_0.\]
The goal of this problem is to find an expression for $F_n$.

\begin{enumerate}
\item Compute the characteristic polynomial of $A$, $\chi_A(X)=det (A-X I_2)$, and its eigenvalues.
\item Is $A$ diagonalizable? Why?
\item If yes, diagonalize $A$: first find the eigenspaces of $A$, then the change of basis matrix $P$ and its inverse.   
\item Compute $A^n$. 
\item Give an expression for $F_n$.
\end{enumerate}

\newpage
\

\newpage
\

%%%%%%%%%%%%%%%%%%%%%%%5

	\thispagestyle{empty}
%	\vskip 0.1in
%\vskip 1.5in

	\thispagestyle{empty}
%\vskip 0.1in
\end{enumerate}
\end{document}
