\documentclass[reqno,oneside,a4paper,11pt]{amsart}

\input{macro}



\title[Going-Down functors and the K\"unneth-formula]{\texorpdfstring{Going-Down functors and the Künneth-formula for crossed products by ample groupoids}{Going-Down functors and the Künneth-formula for crossed products by ample groupoids}}
\author{Christian B\"onicke}
\address{Mathematisches Institut der WWU M\"unster,
	\newline Einsteinstrasse 62, 48149 M\"unster, Germany}
\email{c.boenicke@wwu.de}

\author{Clément Dell'Aiera}
\address{Department of Mathematics, University of Hawaii
	\newline 2565 McCarthy Mall, Keller 401A Honolulu HI 96822.
}
\email{dellaiera@math.hawaii.edu}

\thanks{Supported by Deutsche Forschungsgemeinschaft (SFB 878).}
\subjclass[2010]{22A22, 46L05, 46L35}
\keywords{Ample groupoid,}

\begin{document}
\maketitle
\begin{abstract}
		We study the connection between the Baum-Connes conjecture for an ample groupoid $G$ with coefficient $A$ and the Künneth formula for the $\K$-theory of tensor products by the crossed product $A\rtimes_r G$. To do so we develop the machinery of Going-Down functors as pioneered in the group case by Chabert, Echterhoff and Oyono-Oyono for ample groupoids. Using this machinery we prove that the topological $\K$-theory of an ample groupoid $G$ is continuous with respect to inductive limits of the coefficient algebra. We also prove that the Uniform Roe algebra of a coarse space which uniformly embeds into a Hilbert space satisfies the Künneth formula.
\end{abstract}

\section{Introduction}
\input{Intro}	

\section{Preliminaries on groupoids and $G$-algebras}
\input{Preliminaries}

\section{Inductive limits of $G$-algebras}
\input{Inductive}
	
\section{Going-Down Functors}
\input{GDFunctors}
	
\section{Continuity of Topological K-theory}
\input{Continuity}
	
\section{A Mixed Künneth Formula}
\input{MixedKunneth}	
	
\section{Applications}
\input{Examples}
	
	\ \newline
	{\bf Acknowledgments}. The content of this paper covers some results from the author's doctoral thesis. The first one would like to thank his supervisor Siegfried Echterhoff for his support and advice. The second author expresses his gratitude to his advisor Hervé Oyono-Oyono for his patience and guidance, and to Rufus Willett, who was kind enough to read and comment the first drafts of this work. 
	
\bibliographystyle{amsalpha}
\bibliography{Literatur,biblio2}

\end{document}