\section{Standard modules}

The aim of this section is to develop a notion of non-degenerate standard modules over a groupoid analogous to non-degenerate standard modules over coarse spaces. \\

Let us first recall the coarse case. Let $X$ be a discrete metric space with bounded geometry. 

\begin{definition}
A $X$-module is a Hilbert space $H_X$ equipped with a $*$-representation $\phi : C_0(X) \rightarrow \mathcal L(H_X)$. The $X$-module $(H_X,\phi)$ is said to be :\\

\begin{itemize}
\item[$\bullet$] standard if $\phi(C_0(X))H_X$ is dense in $H_X$,
\item[$\bullet$] non-degenerate if $\forall f \in C_0(X), \phi(f)\in \mathfrak K (H_X) \implies f=0$.
\end{itemize}
\end{definition}

The usefulness of n.d.s. $X$-modules comes from the following lemma :

\begin{lem}
Let $X$ and $Y$ be two discrete metric spaces with bounded geometry, and $h : X\rightarrow Y$ a coarse map. Then, for any two standard modules $H_X$ and $H_Y$ over $X$ and $Y$ respectively, there exists an isometry which covers $h$, i.e. for any $\epsilon >0$, there exists $V\in \mathcal L(H_X,H_Y)$ such that 
\[\text{supp }V \subseteq \{(x,y)\in X\times Y, d(h(x),y)<\epsilon\}.\]
\end{lem}

\textbf{Remark :} We can induce $V$ on the Roe algebras by $\forall T\in C^*(X,H_X), Ad_V(T) := V T V^* \in C^*(Y,H_Y)$, and the preceding lemma entails that \[(Ad_V)_* : K(C^*(X,H_X))\rightarrow K(C^*(Y,H_Y))\] only depends on the coarse class of $h$. We directly see that the $K$-theory of the Roe-algebras of $X$ do not depend on the standard modules if they are n.d.s. : one just need to take an isometry covering the identity. \\

We can actually show that taking the Roe algebra is a functor. Choose, for any coarse space $X$ a n.d.s. $X$-module $H_X$, and consider the category $Coarse$ of coarse spaces with morphisms coarse maps, and the category $KK$ with objects $C^*$-algebras, and morphisms defined by $KK$-theory, $Hom_{KK}(A,B)=KK(A,B)$. Then $ X \mapsto C^*(X,H_X) $ and $\left(h:X \rightarrow Y\right) \mapsto (Ad_V)_*\in KK(C^*(X,H_X),C^*(Y,H_Y))$ defines a functor $Coarse \rightarrow KK$, which does not depend on the choices $X\mapsto H_X$ being made.\\

We will focus ont the following result :

\begin{thm}
Let $X$ be a finite simplicial complex, and $B$ a $C^*$-algebra. There exists $\varepsilon_0\in (0,\frac{1}{4})$ such that for all $\varepsilon \in (0,\varepsilon_0)$, there exists $R_\varepsilon>0 $ s.t. 
\[\forall R\in (0,R_\varepsilon),\  Ind_{X,B}^{\varepsilon, R} : KK(C(X),B)\rightarrow K^{\varepsilon,R}(B\otimes \mathfrak K(H_X))\] 
is an isomorphism.
\end{thm}

We wish to prove a similar result for "nice" groupoids. Let us recall the definition of $G$-simplicial complex from \cite{TuBC2}.

\begin{definition}
Let $G$ be a locally compact groupoid. A $G$-simplicial complex of dimension less than $n$ is a triple $(Z,\Delta, p)$ where
\begin{itemize}
\item[$\bullet$] $Z$ is a locally compact space of vertices and $p: Z \rightarrow G^{(0)}$ a locally injective map, which is an anchor map for an action of $G$, 
\item[$\bullet$] $\Delta$ is a closed $G$-invariant subset of the probability measures $P(Z)$ on $Z$, equipped with the weak-$*$ topology, with the property that every element of $\Delta$ has a support contained in a fiber of $p$ and has at most $n+1$ elements. Such a support is call a simplex of $\Delta$. Moreover, if $\nu\in \Delta,\mu \in P(Z)$ and $supp(\mu)\subseteq supp(\nu)$ then $\mu\in \Delta$.
\end{itemize}
\end{definition}

The first step is to defined what is a s.n.d. $G$-module.

\begin{definition}
A s.n.d. $G$-module is a triple $(E,\phi,V)$ where $E$ is a $C_0(G^{(0)})$-algebra, $\phi : C_0(G^{(0)})\rightarrow \mathcal L(E)$ is a $*$-representation and $V$ is an action of $G$ on $E$ such that
\begin{itemize}
\item[$\bullet$] $E$ decomposes as a external tensor product $E\simeq E^{(0)}\otimes E^{(1)}$ of $G$-modules such that there exists $\phi : C_0(G^{(0)})\rightarrow \mathcal L(E^{(0)})$ and $\phi= \phi_0\otimes id_{E^{(1)}}$
\item[$\bullet$] No non-zero function of $C_0(G^{(0)})$ acts as a compact operator via $\phi_0$, and $\overline{\phi_0(C_0(G^{(0)}))E^{(0)} }= E^{(0)}$
\item[$\bullet$] For all compact subgroupoids $K$ of $G$, there exists an isomorphism of $K$-modules $\text{Res}_K^G E^{(1)} \simeq L^2(K)\otimes H_K$ where $H_K$ is a separable Hilbert space.
\end{itemize}
\end{definition}

Now we want to show the following :

\begin{lem}
Let $G$ be a locally compactly induced groupoid, and $E,E'$ any two s.n.d. $G$-modules, then for any compact subset $K$ of $G$, there exists an isometry $V\in \mathcal L(E,E')$ such that 
\[supp\ V \subseteq (s\times r)(K). \]
\end{lem}

\begin{dem}
Let $E$ a n.d.s. $G$-module, and decompose the base space $G^{(0)}$ into $G$-invariant subset which are locally induced by compact subgroupoids of $G$ :
\[G^{(0)} = \cup_{j=1}^J G\times_{K_j} U_j.\]
By the third hypothesis of being s.n.d., there exist a Hilbert space $H_j$ and an isomorphism of Hilbert modules $F_j :\text{Res}_{K_j}^G E^{(1)} \rightarrow  L^2(K_j)\otimes H_j$, but the induction $\text{Ind}_{K_j}^G L^2(G/K_j)\otimes L^2(K_j)\otimes H_j$ is non canonically isomorphic to $L^2(G)\otimes H_j$, so that $E$ is isomorphic to $E^{(0)}\otimes L^2(G)\otimes H_j$.\\
\qed
\end{dem}

\begin{cor}
Let $G$ and $G'$ two locally compactly induced groupoids, $E,E'$ two s.n.d. modules over $G$ and $G'$ respectively and $(Z,p,p')$ a generalized morphism from $G$ to $G'$ which respects condition ??. For any compact subset $K$, there exists an isometry $V\in \mathcal L(E,E')$ such that
\[supp\ V \subseteq (p\circ (p')^{-1}(s(K))\times r)(K). \]
\end{cor}

