\section{English Notes}

In a serie of papers, H. Oyono-Oyono and G. Yu have defined a controlled version of operator $K$-theory, ~\cite{OY1}~\cite{OY2}~\cite{OY3}, that allows them to define a quantitative and local assembly map, and a related Baum-Connes Conjecture. The aim of this work is to extend their work to the realm of groupoids. In a second part, we shall see how this setting can help us understand better the relation between the coarse-Baum-Connes conjecture and the Baum-Connes Conjecture with coefficient for groupoids. Indeed, in ~\cite{TuBC} and ~\cite{SkTuYu}, G. Skandalis, J-L.Tu and G. Yu proved that there is a commutative diagramm
\[\begin{tikzcd}
K_*(X) \arrow{r}{A}\arrow{d}{\simeq} & K_*(C^*X)\arrow{d}{\simeq} \\
K_*(\mathcal E \Gamma)\arrow{r}{\mu_r} & K_*(C_r \Gamma)
\end{tikzcd}\]
where :
\begin{itemize}
\item the left sides are $K$-homology of certain spaces, the left sides are $K$-theory of certain $C^*$-algebras,
\item the first line is the coarse assembly map associated to a coarse space $X$, the second being the assembly map for groupoids associated to the coarse groupoid of $X$, namely $\Gamma = G(X)$,
\item the vertical arrows are isomorphisms on the level of $KK$-groups. The left one will be studied later, the right one derives from an isomomorphism on the level of the $C^*$-algebras. Indeed, it has been shown that the Roe algebra is $*$-isomorphic to the crossed product of $l^\infty (X)$ by $\Gamma$ : $C^*(X) \simeq l^\infty(X)\times \Gamma$.\\
\end{itemize}

We shall see that this relation is already true "locally" and factorises through quantitative $K$-theory. Locally here means that we can factorize the assembly map through $KK(C_0(P_d(X),B)$. Indeed, the $K$-homology can be expressed as an inductive limit 
\[K_*(X,B)=\varinjlim_{d\rightarrow \infty}  KK(C_0(P_d(X)), B ) \quad \text{and}\quad\] 
hence the local. \\

The local quantitative assembly maps defined in \cite{OY2} are of the form
\[KK^F(C_0(P_d(F)), B  ) \rightarrow K^{\epsilon, r}_*(B\times_r \Gamma)\]
where $F$ is a finite group. \\

We will be using the bivariant functor $KK^\Gamma$ introduced by P-Y. Le Gall in his thesis ~\cite{LeGall}, which is a generalization of Kasparov's bifunctor for the case where $\Gamma$ is a Hausdorff locally compact groupoid with Haar system. As for the $KK$-theory for Banach algebras introduced by V. Lafforgue~\cite{Lafforgue}, there is no (not yet?) a Kasparox product in quantitative $K$-theory. The crucial point to define an assembly map is the existence of a morphism 
\[\hat J : KK^{\Gamma}(A,B)\rightarrow Hom^*(\hat K_*(A),\hat K_*(B))\]
which allows us, for every element $x\in K_*(A)$, to consider the related index
\[Ind_x \left\{ \begin{array}{ccc} KK_*(A,B) & \rightarrow  & K_*(B)\\
	z & \mapsto & \hat J(z)(x)
\end{array}\right.\]
to construct $\hat J$, we will mimic the construction for $\mathcal J$ in ~\cite{OY2}, which gives the right morphism when considering finite groups. The starting point is the following 

\begin{lem}
Let $\Gamma$ be a Hausdorff locally compact groupoid with Haar system. Then, if $A$ is a $\Gamma-C^*$-algebra, forming the reduced (and maximal) crossed product $A\times_r \Gamma$ is functorial in $A$. Moreover, if $\Gamma$ is \textit{étale}, then it preserves short semi-split filtered exact sequences of $\Gamma-C^*$-algebras, meaning that if 
\[\begin{tikzcd}[column sep = small] 0\arrow{r} & A' \arrow{r} & A\arrow{r} & A'' \arrow{r} & 0\end{tikzcd}\]
is a semi-split filtered exact sequence of $\Gamma-C^*$-algebras, then 
\[\begin{tikzcd}[column sep = small] 0\arrow{r} & A' \times_r \Gamma\arrow{r} & A\times_r \Gamma\arrow{r} & A'' \times_r \Gamma\arrow{r} & 0\end{tikzcd}\]
is too.
\end{lem}

\begin{dem}
Let 
\[\begin{tikzcd}[column sep = small] 0\arrow{r} & A' \arrow{r}{\Psi} & A\arrow{r}{\Phi} & A'' \arrow{r} & 0\end{tikzcd}\]
be a semi-split filtered exact sequence of $\Gamma-C^*$-algebras.\\

Let $f\in C_c(\Gamma, A)$ such that $\Phi_\Gamma(f)=0$. For every $\gamma \in \Gamma$, there exists a unique $g(\gamma)\in A'$ such that $\Psi(g(\gamma))=f(\gamma)$. But, as $\Psi$ and $\Phi$ commute with the action of $\Gamma$, we have $g(\gamma'^{-1}\gamma)=\gamma' . g(\gamma)$, so that $g$ is continuous.\\

Let $a\in A\times \Gamma$ such that $\Phi_\Gamma(a)=0$. We can approximate $a$ by a sequence of $f_n\in C_c(\Gamma,A)$. But, with the preceeding work on compactly supported continuous functions, there exist a sequence $g_n\in C_c(\Gamma, A')$ such that :
\[f_n = \Psi(g_n)+\sigma\circ \Phi(f_n).\]
Moreover, $\text{Im}\ \Psi$ is a closed ideal in $A$, and $\lim ||f_n-\Psi(g_n)||=0$ so that $a\in \text{Im} \ \Psi$ : the sequence is exact in the middle.
\qed
\end{dem}

\subsection{}
Let $X$ be a discrete metric space with bounded geometry and $\Gamma$ its coarse groupoid. We denote by $\tilde A $ the $C(\Gamma)$-algebra $C_0(P_d(\Gamma))$, and by $A$ the $C^*$-algebra $C_0(P_d(X))$. As $P_d(\Gamma)$ is equivariantly homeomorphic to $\beta X \times P_d(X)$, the fiber $\tilde A_x$ is isomorphic to $A$ as a $C^*$-algebra.\\
 
\begin{lem}
Let $B$ be a $C^*$-algebra and $x\in X$. The morphism of groupoids $\iota : \{e_x\}\rightarrow \Gamma$ induces an isomorphism in $KK$-theory 
\[\begin{tikzcd}[column sep = small] KK_*^\Gamma(\tilde A, l^\infty(X, B))\arrow{r}{\simeq} & KK_*(A, B)\end{tikzcd}.\]
\end{lem}

\begin{dem}
Let us first check that the fiber over $x\in X$ of $\tilde B :=l^\infty(X,B)$ is $B$ : easily, if $I_x$ denotes the kernel of the evaluation map $\tilde B \rightarrow B$ at $x$, $\tilde B_x = \tilde B / I_x \tilde B\simeq B $. Moreover, as $\tilde A_x \simeq A$, functoriality assures that $\iota$ induces $\iota^* : KK_*^\Gamma(\tilde A, l^\infty(X, B))\rightarrow KK_*(A, B)$.\\

We can now construct an explicit $R$ inverse for $\iota^*$. Let $z=(\hat H_{\tilde B},\Phi, T)\in \mathbb E^\Gamma(\tilde A,\tilde B)$ be a $K$-cycle. By stabilization theorem, we can suppose that the Hilbert $\tilde B$ module is in canonical form, that is the standard separable Hilbert module over $\tilde B$ with usual grading. We will also suppose that $T$ is $\Gamma$-equivariant, which is always true up to compact perturbation. The image of $z$ under $R$ is defined to be its restriction to $x$, $(\hat H_B,\Phi_x,T_x)$. This definition gives immediatly $R\circ \iota^* = 1$. Now let $V : s^* \hat H_{\tilde B}\rightarrow \hat H_{\tilde B}$ be the unitary implementing the action of $\Gamma$ on $\hat H_{\tilde B}$. The equivariance of $T$ can be written as 
\[V_\gamma T_{s(\gamma)} V_\gamma^* = T_{r(\gamma)}\quad,\forall \gamma \in \Gamma. \]
If $T' = \iota^*\circ R(T)$, it is the constant operator with fiber $T_x\in \mathcal L_B(\hat H_B)$ on the trivial Hilbert module $\bigoplus_{y\in X}(H_{\tilde B})_x $. Define $V=\bigoplus_{\gamma \in \Gamma} V_\gamma$. It is unitary and intertwines $T$ and $T'$, i.e. the cycles are homotopic and $\iota^*\circ R = 1$.

\qed
\end{dem}

\begin{lem}
Let $B$ be a coefficient $C^*$-algebra. The uniform Roe algebra of $X$  and the Roe algebra of $X$ are $*$-isomorphic to crossed-product algebras by $\Gamma$, respectively : 
\[\begin{array}{ll} C_u^* (X,B) \simeq l^\infty(X,B) \rtimes \Gamma \\ C^* (X,B) \simeq l^\infty(X,\K\otimes B) \rtimes_r \Gamma \end{array}.\]
\end{lem}

\begin{dem}
A faire
\qed
\end{dem}

This $*$-isomorphism gives an isomorphism at the level of $K$-theory 
\[ K_*(C^* (X,B))\rightarrow K_*(l^\infty(X,\K\otimes B)\rtimes_r \Gamma).\]
These lemmas allows us to state a reffinement of a result of G. Skandalis, J-L.Tu and G. Yu \cite{SkTuYu}, namely that the two isomorphisms described above intertwine the (local quantitative ?) assembly maps for the groupoid $\Gamma$ with coefficients in $l^\infty(X)$ with the coarse assembly map of $X$. (If local and quantitative :) This result at the level of controlled $K$-theory on the right side entails that of \cite{SkTuYu}

\begin{thm}
The following diagram
\[\begin{tikzcd}[column sep = small]
A : KK_*(A,B)\arrow{r}\arrow{d}{\simeq} & K_*(C^*(X,B)) \arrow{d}{\simeq}\\
\mu_{r} : KK^\Gamma \arrow{r} & K_*(l^\infty(X,\K\otimes B)\rtimes_r \Gamma)
\end{tikzcd}\]
commutes, and the vertical arrows are isomorphisms.
\end{thm}



















