\section{The Künneth formula in operator $K$-theory}

In this section, we present a proof of the Künneth formula for some crossed products by an étale groupoid. \\

Recall that for $A$ and $B$ two $C^*$-algebras, $\alpha_{A,B}$ is the homomorphism
\[\alpha_{A,B} : K_*(A)\otimes K_*(B)\rightarrow K_*(A\otimes B) \quad ; \quad (x,y)\mapsto x\otimes   \tau_A(y),\]
where $\tau_A$ is the external Kasparov product.\\

\begin{definition}
A $C^*$-algebra $A$ is said to satisfy the Künneth formula if, for every $C^*$-algebra $B$ such that $K_*(B)$ is a free abelian group, $\alpha_{A,B}$ is an isomorphism.
\end{definition}

If $A$ satisfies the Künneth formula, then, for any $C^*$-algebra $B$, one has the following exact sequence
\[\begin{tikzcd}[column sep = small] 0 \arrow{r} & K_*(A)\otimes K_*(B)\arrow{r} & K_*(A\otimes B) \arrow{r} & Tor(K_*(A),K_*(B))\arrow{r} & 0 \end{tikzcd}\]

The remainder of the section is devoted to prove the theorem \ref{Kunneth}. We first recall the induction and restriction machinery in the context of equivariant $KK$-theory. The important result is lemma \ref{Restriction}, which allows to restrict $KK^G$-elements to compact open subgroupoids under some suitable conditions. We then define a class $\mathcal C$ of groupoids which satisfies these suitable conditions, and give instances of this class. The end of the section is devoted to the proof of the main theorem.

%%%%%%%%%%%%%%%%%%%%%%%%%%
%	INDUCTION	%%
%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \input{Induction}	%
%\input{InductionSimple} %
\input{InductionFinal}
%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Baum-Connes and the Künneth formula}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section, we give the proof of the main result and give some applications.	

\subsection{Proof}

The first step in proving theorem \ref{Kunneth} is to define an analytical version of $\alpha_{A,B}$ when an étale groupoid $G$ is given. More precisely, we first construct a homomorphism $\alpha_{A,B}^G : K_*^{top}(G,A)\otimes K_*(B)\rightarrow K_*^{top}(G,A\otimes B )$, inductive limit of $\alpha_{A,B}^{G,Z} : RK^G(Z,A)\otimes K_*(B)\rightarrow RK^G(Z,A\otimes B )$ where $Z$ runs through $G$-proper $G$-compact spaces. Then we show that the assembly map intertwines $\alpha^{G,P_E(G)}_{A,B}$ and $\alpha_{A\rtimes_r G,B}$.\\

If $A$ is a $G$-algebra, and $B$ a $C^*$-algebra, $A\otimes B$ naturally inherits a $G$-algebra structure with trivial action of $G$ on the $B$ factor. Then $(A\rtimes_r G)\otimes B \cong (A\otimes B)\rtimes_r G$.\\

Let $Z$ be a $G$-proper space. Define the homomorphism :
\[\alpha_{A,B}^{G,Z} : RK^G_*(Z,A)\otimes K_*(B)\rightarrow RK_*^G(Z,A\otimes B) \quad ; \quad (x,y)\mapsto x\otimes_{}   \tau_A(y),\]
which respects inductive limits w.r.t. inclusions of $G$-proper spaces, so that it induces
\[\alpha_{A,B}^G : K_*^{top}(G,A)\otimes K_*(B)\rightarrow K_*^{top}(G,A\otimes B ).\]

To prove theorem \ref{Kunneth}, we will need the following result.

\begin{thm}\label{TopologicalKunneth}
Let $G$ be an étale groupoid in the class $\mathcal C$, and let $E\in\mathcal E$ be a controlled subset of $G$ and $P_E(G)$ be the corresponding Rips complex. If, for all compact open subgroupoids $H$ of $G$ and every $H$-space $V$ such that the anchor map $p : V\rightarrow H^{(0)}$ is locally injective, $\alpha_{A,B}^{H,V}$ is an isomorphism, then $\alpha_{A,B}^{G,P_E(G)}$ is an isomorphism for all $C^*$-algebras $B$ such that $K_*(B)$ is a free abelian group.
\end{thm}

\begin{dem}
Let $Z_0\subseteq Z_1\subseteq ... \subseteq Z_n $ be the skeleton decomposition of $P_E(G)$.\\

Let us prove by induction that $\alpha_j=\alpha^{G,Z_j}_{A,B}$ is an isomorphism. By a standard Mayer-Vietoris type argument, %similar to the proof of theorem \ref{prod}, 
it is sufficient to prove the statement for $j=0$.\\

Let $U\subseteq Z_0$ be a $G$-compact $G$-proper space. By strong properness, $U$ can be finitely covered by open subsets of the type $G \times_H V$. By a standard Mayer-Vietoris argument, we can suppose that there exists a compact open subgroupoid $H$ of $G$ and a compact $H$-space $V$ such that $U = G \times_H V$. The following diagram is commutative :
\[\begin{tikzcd}[column sep = small] 
RK_*^G(U,A)\otimes K_*(B) \arrow{r}{\alpha_{A,B}^{G,U}} \arrow{d}{\text{Res}_H^G} & RK^G(U, A\otimes B) \arrow{d}{\text{Res}_H^G}\\
RK_*^H(V, A)\otimes K_*(B) \arrow{r}{\alpha_{ A,B}^{H,V}} & 
	RK_*^H(V,  A\otimes B)\\
\end{tikzcd}\]

The vertical arrows are isomorphisms by Proposition \ref{Restriction}, the last horizontal one is by hypothesis. Hence $\alpha_{A,B}^{G,U}$ is an isomorphism. By taking the inductive limit on $G$-proper $G$-compact spaces $U\subseteq Z_0$, we get that $\alpha_{A,B}^{G,Z_0}$ is an isomorphism.
\end{dem}

\begin{lem}\label{KunnethLemma}
For every étale groupoid $G$, any $G$-algebra $A$, and any $C^*$-algebra $B$, the following diagram commutes :
\[\begin{tikzcd}
RK_*^G(P_E(G),A)\otimes K_*(B) \arrow{r}{\alpha^{G,P_E(G)}_{A,B}}\arrow{d}{\mu_{G,A}\otimes \text{id}_{K_*(B)}} & 
RK_*^G(P_E(G),A\otimes B) \arrow{d}{\mu_{G,A}} \\
K_*(A\rtimes_r G)\otimes K_*(B) \arrow{r}{\alpha_{A\rtimes_r G,B}} & 
K_*((A\otimes B)\rtimes_r G)\\
\end{tikzcd}\] 
for all $E\subseteq G$ compact. 
\end{lem}

\begin{dem}
Let $z\in RK_*^G(P_E(G),A)$ and $y\in K_*(B)$. As the action of $G$ on $B$ is trivial, $(A\rtimes_r G)\otimes B\simeq (A\otimes B)\rtimes_r G$ so that $j_G(z \otimes \tau_A(y))= j_G(z) \otimes \tau_{A\rtimes_r G}(y)$ holds. This entails
\[\alpha_{A\rtimes_r G, B}(\mu_{G,A}(z)\otimes y)= [\mathcal L_E] \otimes j_G(z)\otimes \tau_{A\rtimes_r G}(y) = 
[\mathcal L_E] \otimes j_G( z\otimes \tau_A(y) ) = \mu_{G,A\otimes B}(\alpha^{G,P_E(G)}_{A,B}(z\otimes y)) ,\]
which is just the statement of the lemma.\\
\qed
\end{dem}

We can now prove the main theorem of the section.

\begin{thm}\label{Kunneth}
Let $G$ be a $\sigma$-compact étale groupoid and $A$ a $G$-algebra. Suppose that 
\begin{itemize}
\item[$\bullet$] $G$ satisfies the Baum-Connes conjecture with coefficients,
\item[$\bullet$] $G$ is in the class $\mathcal C$,
\item[$\bullet$] for every compact open subgroupoid $H$ of $G$ and every $H$-space $V$ such that the anchor map $p : V \rightarrow H^{(0)}$ is locally injective, $\alpha_{A,B}^{H,V}$ is an isomorphism for every $C^*$-algebra $B$ such that $K_*(B)$ is free.
\end{itemize} 
Then $A\rtimes_r G$ satisfies the Künneth formula.
\end{thm}

\begin{dem} %\textit{of theorem \ref{Kunneth}}\\

Let $A$ be a $G$-algebra and $B$ a $C^*$-algebra, seen as a $G$-algebra with trivial action, such that $K(B)$ is free. As $(A\otimes B)\rtimes_r G \cong (A\rtimes_r G)\otimes B$, we will identify them in the remaining of the proof. Let us prove that $\alpha_{A\rtimes_r G,B}$ is an isomorphism.\\

Lemma \ref{KunnethLemma} entails that the following diagram commutes
\[\begin{tikzcd}
K_*^{top}(G,A)\otimes K_*(B) \arrow{r}{\alpha^{G,top}_{A,B}}\arrow{d}{\mu_{G,A}\otimes \text{id}_{K_*(B)}} & 
K_*^{top}(G,A\otimes B) \arrow{d}{\mu_{G,A}} \\
K_*(A\rtimes_r G)\otimes K_*(B) \arrow{r}{\alpha_{A\rtimes_r G,B}} & 
K_*((A\otimes B)\rtimes_r G)
\end{tikzcd}\]
with vertical arrows being isomorphism, because $G$ satisfies Baum-Connes with coefficients. Thus, it suffices to show that $\alpha^{G,P_E(G)}_{A,B}$ is an isomorphism for every compact $E\subset G$. But this follows from the last two hypothesis of the theorem together with Theorem \ref{TopologicalKunneth}.\\ 
\qed
\end{dem}

\begin{rk}
For principal and transitive groupoids, the third condition in theorem \ref{Kunneth},
\begin{center} 
``$\alpha_{Res_H^G(A),B}^{H,V}$ is an isomorphism'',
\end{center}
reduces to ``$A$ satisfies the Künneth formula". Indeed, the only non trivial subgroupoid is the trivial one.
\end{rk}

\begin{rk}
We would like to comment on the third condition of theorem \ref{Kunneth}, namely:
\[\text{``for every compact open subgroupoid }H \text{ of } G \text{ and every }H \text{-space }V \]
\[\text{ such that the anchor map }p : V \rightarrow H^{(0)}\text{ is locally injective, }\]
\[\alpha_{A,B}^{H,V}\text{ is an isomorphism for every } C^*\text{-algebra} B \text{ such that $K_*(B)$ is free".}\]
In the case of a group, a locally injective anchor map impose for $V$ to be a disjoint union of points so that the condition reduces to $A\rtimes_r H$ satifies the Künneth formula. \\

We can have a similar statement in the groupoid setting if we suppose that there exists an $H$-equivariant open covering of $V$ such that $p_{|U}$ is injective. The Mayer-Vietoris exact sequence associated to any finite such covering, and then taking the inductive limit, shows that the condition reduces to $A\rtimes_r H$ satisfies the Künneth formula.  
\end{rk}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%  EXAMPLES   %%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Examples}

A natural question is to find examples of $C^*$-algebras for which theorem \ref{Kunneth} ensures the Künneth formula, without this being a consequence of previous known results \cite{RosenbergKunneth},\cite{ChabertEOY},\cite{OY4}. Unfortunately, the author was not able to come up with such an example. We will nevertheless list several applications, as it shows the interest of the Going-Down principle extended to groupoids, even if the results are derivable from the existing litterature.\\

Let $X$ be a countable discrete metric space with bounded geometry. In \cite{SkTuYu} is constructed the coarse groupoid $G(X)$ associated to $X$ where it is shown to be locally compact, ample, Hausdorff and principal. Thus $G(X)$ is in the class $\mathcal C$. Moreover, if $X$ admits a coarse embedding into a Hilbert space iff $G(X)$ is a-T-menable, which implies (\cite{TuThese}) the Baum-Connes conjecture with coefficients for $G(X)$. The coarse groupoid is principal, and has only two invariant subsets and thus only has only three subgroupoids: $G^{(0)}= \beta X$, $G(X)_{|\partial X}$ and $G(X)_{|X}$. As soon as $X$ is not bounded, none of the last two are compact. So the last condition of theorem \ref{Kunneth} reduces to the usual Künneth formula for $A$, and we get the following application. \\

\textbf{Application 1:} If $X$ admits a coarse embedding into a Hilbert space and $A$ is a $C^*$-algebra satisfying the Künneth formula, then $A\rtimes_r G(X)$ satisfies the Künneth formula. In particular the uniform Roe algebra $C_r^*(G(X))\cong C_u^* (X) $ satisfies the Künneth formula.  \\

Of course, this is not new for complex coefficients: $G(X)$ being a-T-menable implies that $C_r^*(G(X))$ is in the bootstrap class. Notice that this fails for the Roe algebra $C^*(X) \cong l^\infty (X, \mathfrak K(H)) \rtimes_r G(X)$, as $l^\infty (X, \mathfrak K(H))$ fails to satisfy the Künneth formula. \\ 

Let $\Gamma$ an infinite hyperbolic property T group, and $\Omega$ a Cantor space equipped with an action of $\Gamma$ by homeomorphisms. Then the action groupoid $X\rtimes \Gamma$ is ample, thus in the class $\mathcal C$ by proposition \ref{ampleC}. By Lafforgue's work \cite{lafforgue2012conjecture}, $\Gamma$ satisfies the Baum-Connes conjecture with coefficients so the isomorphism \[A\rtimes_r (\Omega\rtimes \Gamma) \cong (A\otimes C(\Omega))\rtimes_r \Gamma \]
ensures that $\Omega\rtimes \Gamma$ satisfies the Baum-Connes conjecture with coefficients. The last condition will be automatic if $A\rtimes_r H$ satisfies the Künneth formula for $H$ a compact open sugroupoid, which is of the form $U\rtimes F $ with $U $ a $\Gamma$-invariant compact open subset of $\Omega$ and $F$ a finite subgroup $F$ of $\Gamma$. Thus theorem \ref{Kunneth} ensures the following.\\

\textbf{Application 2: } If $\Gamma$ is an infinite hyperbolic property T group, $\Omega$ a Cantor $\Gamma$-space, and $A$ is a $C^*$-algebra such that $(A\otimes C(U))\rtimes_r F$ satisfies the Künneth formula for every $\Gamma$-invariant compact open subset $U$ of $\Omega$ and any finite subgroup $F$ of $\Gamma$, then $A \rtimes_r (X\rtimes \Gamma)$ satisfies the Künneth formula. \\ 

Here again, this result is not new and is a consequence of the Going Down principle (\cite{ChabertEOY}) applied to $\Gamma$. We can also blend the two last examples together: if $\Gamma$ is a discrete group, then it has only one coarse class of left invariant metric, and we denote by $|\Gamma|$ the associated coarse metric space. It is shown in \cite{SkTuYu} that the coarse groupoid is an action groupoid, more precisely \[G(|\Gamma|) \cong \beta |\Gamma| \rtimes \Gamma.\]
This groupoid is again in the class $\mathcal C$ and satisfies Baum-Connes with coefficients. The third condition follows as earlier.\\

\textbf{Application 3:} If $\Gamma$ is a hyperbolic group and $A$ is a $C^*$-algebra such that $(A\otimes C(U))\rtimes_r F$ satisfies the Künneth formula for every $\Gamma$-invariant compact open subset $U$ of $\beta |\Gamma|$ and any finite subgroup $F$ of $\Gamma$, then $A\rtimes_r G(X)$ satisfies the Künneth formula. In particular the uniform Roe algebra \[l^\infty(\Gamma)\rtimes_r \Gamma\cong C_u^* (\Gamma)\] satisfies the Künneth formula.  

\subsubsection{Hyperbolic groupoids}
Recall the following definition from \cite{LaffOY}.

\begin{definition}\label{hyperbolicLaff}
Let $G$ be a Hausdorff \'etale groupoid. $G$ is said to be:
\begin{itemize}
\item[$\bullet$] \textit{hyperbolic} if there exists a positive number $\delta$ and a right invariant length $l$ on $G$ such that $(G_x, l_x)$ is a $\delta$-hyperbolic $\delta$-geodesic space for every $x\in G^{(0)}$,
\item[$\bullet$] \textit{with controlled growth} if there exist positive constants $\alpha $ and $\beta$ such that the balls 
\[B(g,R) = \{ g' \in G_x : d_x(g,g'))\}\] 
for $s(g)=x$ satisfy \[|B(g,R)| \leq \alpha e^{\beta l(g)}.\]
\end{itemize}
\end{definition}

The main result of \cite{LaffOY} is the following theorem:

\begin{thm}[Thm. $4.0.1$, \cite{LaffOY}]
Let $G$ be a Hausdorff \'etale hyperbolic groupoid with controlled growth. If there exists a proper $G$-algebra $A$ and elements 
\[\alpha \in KK^G(C_0(G^{(0)}) , A) \quad \text{and} \quad \beta\in KK^G(A, C_0(G^{(0)}))\]
such that $\gamma = \alpha \otimes_A \beta\in KK^G(C_0(G^{(0)}),C_0(G^{(0)}))$ satisfies:
\begin{itemize}
\item[$\bullet$] there exists a sequence of right invariant length $(l_i)_i$ converging uniformly to zero on every compact subset of $G$ such that 
\[\iota(\gamma) = 1 \in KK^{G,l_i}_{ban}C_0(G^{(0)}),C_0(G^{(0)}))\] 
\item[$\bullet$] for every $G$-compact subset $Z \subseteq \underline E G$ with anchor map $q: Z \rightarrow G^{(0)}$, 
\[q^*(\gamma) = 1 \in KK^{Z\rtimes G}(C_0(Z),C_0(Z)),\]
\end{itemize}
then the assembly map
\[\mu_{G,r} : K^{top}(G)\rightarrow K(C_r^*(G))\]
is an isomorphism.
\end{thm}

In \cite{nekrashevych} is given the definition of a hyperbolic pseudogroup. $S$ is compactly generated if there exists an open relatively compact transversal $T$ of $G(S)$ and a symmetric finite set $F$ such that
\begin{itemize}
\item[$\bullet$] any $[x,\phi]$ such that $x, \phi(x)\in T$ decomposes as a product of elements of $F$,
\item[$\bullet$] every element $\gamma \in F$ is the restriction of some $[x,\phi]$ with the domain and the range of $\gamma $ are relatively compacts whose closure sits inside the domain and the range of $\phi$ respectively. 
\end{itemize}

\begin{definition}
A compactly generated pseudo group is hyperbolic if there exists a open relatively compact transversal $T$ and ...
\end{definition}

If $S$ is hyperbolic in this sense, then $G(S)$ is hyperbolic in the sense of definition \ref{hyperbolicLaff}. Moreover, the space $X$ being the base space of the groupoid, $G(S)$ is ample as soon as $X$ is totally disconnected. Any reduced $C^*$-algebra of a compact groupoid satisfies the Künneth formula, because it is of type I. The only condition that remains to be proved is that $G(S)$ satifies the Baum-Connes conjecture for any coefficient $B$ a trivial $G$-algebra.  

\subsubsection{HLS groupoids}

Problem: $\Gamma$ is amenable iff $G_{\mathcal N}$ is. What about a-T-menabilty?

If $\Gamma $ has $T$, then if $\mu_\Gamma$ is injective, $\mu_G  $ is not surjective. So if $\Gamma$ hyperbolic, the HLS groupoid will not satisfy the Baum-Connes conjecture.
























