\subsection{Groupoids and approximation properties}

The following projects revolve around the idea of building $C^*$-algebras with exotic properties using topological groupoids and $*$-representations of their convolution algebra. We make intensive use of two classes of examples: \textit{coarse groupoids} and \textit{HLS groupoids}. Let us describe a particular case of coarse groupoids, and the associated HLS groupoid. Let $\Gamma$ be a finitely generated group together with a decreasing sequence of finite index normal subgroups $N_{i+1}\unlhd N_i$ such that $\cap N_i = 1$. Denote by $\Gamma_n$ the finite group $\Gamma/ N_n$.
\begin{itemize}
\item[$\bullet$] The HLS groupoid $G_{\mathcal N}(\Gamma)$ is a group bundle with base space the one space compactification $\N \cup \{\infty\}$. The fiber is the finite group $\Gamma_n$ over finite places, and $\Gamma$ at $\infty$. The topology is made is such a way that the finite fibers ``converge" to the whole group.  
\item[$\bullet$] The coarse groupoid, in that case, is the groupoid of the action of $\Gamma$ on $\beta X$, the Stone-\v{C}ech compactification of $X$. Here $X$ is the disjoint union $X= \coprod_{n\in \N} \Gamma_n$ of all the finite groups $\Gamma_n$. They are seen as metric spaces with the help of the word metric coming from a fixed generating set, and the total metric satisfies $\lim d(\Gamma_i, \Gamma_j)= \infty$ when $i+j \rightarrow \infty$. The action of $\Gamma$ by translation is extended to the compactification.  
\end{itemize}

One can for instance take $\Gamma = SL_2(\Z) $, $p$ any prime number, and $\Gamma_n = SL_2(\Z / p^n \Z) $. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection*{Property T}

\textit{with Rufus Willett, University of \Hawaii at M\={a}noa}\\

In \cite{DellWillett}, Rufus Willett and I introduced a topological version of Property (T) for topological groupoids. This definition generalizes that of groups, but also recover \textit{Geometric Property (T)}, defined by Willett and Yu in \cite{WillettYu} for metric spaces with bounded geometry. It also is related to property $( \tau )$, a representation theoretic property for residually finite groups, giving a criterion to build expanders, and to \textit{measurable Property T} defined by Anantharaman-Delaroche in \cite{anantharamanT}. These connections provide evidence that our definition is a good generalization, but its real interest lies in the following results.\\
\begin{itemize}
\item[$\bullet$] In the \'etale case, property (T) can be characterized as a spectral gap condition for operators analogous to the Laplacian on a compactly generated \'etale groupoid. This allows one to characterize property (T) as a spectral gap condition and the existence of a Kazdhan projection. \\
\item[$\bullet$] Property (T), together with some technical assumptions, leads to \textit{failure of inner-exactness}. We show that this result holds for the coarse groupoid associated to an expander, and to the HLS groupoid associated to a residually finite group with property $(\tau )$. \\
\end{itemize}
In ongoing work, we try to apply topological property (T) to failure of K-exactness. For instance, it is shown by \v{S}pakula in \cite{SpakulaNonexact} that residually finite groups satisfying a strengthening of property $(\tau)$ have their uniform Roe algebra, which is a groupoid reduced $C^*$-algebra in disguise, are not $K$-exact. This suggest that a stronger form of topological property (T) would lead to failure of $K$-exactness for the reduced $C^*$-algebra of our groupoid. %We can aleady show this for uniform Roe algebras of some expanders. 

\begin{project}
Finding a condition for compactly generated \'etale groupoids which, together with property (T), ensures that its reduced $C^*$-algebra is not $K$-exact. 
\end{project}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Exhaustivity of representations}

\textit{with Yu Qiao, Shaanxi Normal University}\\

Motivated by questions coming from spectral theory of N-body Hamiltonians, and characterizations of Fredholm integral operators and Toeplitz operators, Nistor and Prudhon introduced in \cite{NistorPrudhon} the concept of \textit{exhaustive families of representations}. A family of $*$-representations of a $C^*$-algebra $A$ is \textit{exhaustive} if every irreducible $*$-representation is weakly contained in one of the representations of the family.\\

In particular they prove that, for a groupoid with amenable isotropy groups that satisfies the Effros-Hahn conjecture, the family of regular representations is exhaustive for the maximal $C^*$-algebra of the groupoid. This result has for consequence a famous result of Exel \cite{exel2014invertibility} about invertibility of elements of amenable groupoids $C^*$-algebras.\\

We are interested to applications of exhaustivity to \textit{Roe algebras} and \textit{HLS groupoids}. Indeed, Skandalis, Tu and Yu defined in \cite{SkTuYu} a so-called \textit{coarse groupoid} $G(X)$ associated to a coarse metric space $X$, whose reduced $C^*$-algebra coincides with the uniform Roe algebra of $X$. This groupoid has features very similar to \textit{Fredholm groupoids}, intensively used in index theory: the base space $G^0 = \beta X$ has a dense open subset $U=X$ such that $G_{|U}\cong U\times U$. We denote by $F$ the boundary $\beta X - X$.

\begin{project}
Find conditions ensuring that the family of regular representations restricted to the boundary $\{\lambda_x\}_{x\in F}$ is exhaustive and/or giving an isomorphism $C_r^*G_F \cong C^*_r G / C^*_r G_U$.
\end{project}
 
For instance, we already know that this fails for coarse groupoids of some expanders, and HLS groupoid of non amenable groups. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Matui's conjecture}

\textit{with Christian B\"onicke, School of Mathematics and Statistics of the University of Glasgow}\\ 

In \cite{matui2016etale}, Matui stated two conjectures about the Crainic-Moerdijk homology (as defined in \cite{crainic2000homology}) and the $K$-theory groups of nice ample essentially principal and minimal groupoids. The first one, the HK conjecture, predicts that 
\[K_i (C_r^*(G)) \cong \bigoplus_k H^{2k+i}(G)\quad i=0,1.\]

While the conjecture was proven for particular cases (see \cite{ortega2018homology}, \cite{farsi2018ample} for recent results, and  \cite{MatuiSurvey} for a survey), a counterexample was given by Scarparo in \cite{scarparo2018homology}. The groupoid is obtained using \textit{odometers}, i.e. $G=\Omega \rtimes \Gamma$, where $\Gamma$ is the infinite dihedral group $\Z\rtimes \Z_2$ and the action is given by shift on $\Omega=\varinjlim \Gamma/ \Gamma_i$, $\Gamma_j = n_j \Z \rtimes \Z$.\\

We suggest to look at this conjecture for coarse groupoids. 

\begin{project}
For a metric space $X$ with bounded geometry, compute the homology of the groupoids $G(X)$ and compare it to the $K$-theory of the uniform Roe algebra $C^*_u(X)$. In other words does Matui's conjecture hold for coarse groupoids?
\end{project}

These computations should be carriable in some general cases, for instance in the presence of finite asymptotic dimension. In that case, the $K$-theory is computable since the Baum-Connes conjecture holds, and the homology can be computed using coarse homology (see chapter 7 of \cite{NowakYu}). We also propose to start the computations with HLS groupoids and coarse groupoids associated to box spaces. This should be seen as an analog of Scarparo's counterexamples.

\subsubsection*{Other}

I know that groupoids are appearing in a lot of other parts of operator algebras, and I would be very happy to learn about higher rank graphs $C^*$-algebras or semi-group $C^*$-algebras for instance.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Controlled $K$-theory}

Controlled, or quantitative, $K$-theory is a refinement of operator $K$-theory that has been developed following the celebrated proof of the Novikov conjecture for groups with finite asymptotic dimension by Guoliang Yu \cite{Yu1}. In the course of the proof, some groups appear built from almost-projections and almost-unitaries, with finite propagation, of the Roe algebra $C*(X)$ of a coarse space $X$. These groups are in essence $K$-theory groups with the added possibility of controlling the propagation of the classes, propagation coming from the distance function. This allows one to apply \textit{controlled cutting and pasting} techniques to compute the $K$-theory groups of $C^*(X)$, i.e. Mayer-Vietoris like exact sequences, but involving \textit{almost ideals} instead of genuine ideals. In the case of finite asymptotic dimension, these ideals reduce to finite dimensional $C^*$-algebras, i.e. matrix algebras.\\

In \cite{OY1}, Oyono-Oyono and Yu applied this idea to the computation of the $K$-theory of the Roe algebras of some expanders. They formalized quantitative $K$-theory for $C^*$-algebras similar to reduced $C^*$-algebras of groups $C^*_r(G)$ and Roe algebras $C^*(X)$ in \cite{OY2}, and in \cite{dell2018controlled}, I generalized this approach to the setting of groupoid $C^*$-algebras and quantum groups, and general coarse spaces. These techniques were also applied to computations in $K$-theory:\\
\begin{itemize} 
\item[$\bullet$] Guentner, Willett and Yu proved in \cite{GWY2} the Baum-Connes conjecture for group actions which have \textit{finite dynamical complexity}. This is a translation in the setting of topological group actions of \textit{finite decomposition complexity}, a weakening of \textit{finite asymptotic dimension}.\\   
\item[$\bullet$] Oyono-Oyono and Yu proved the the K\"unneth formula \cite{oyono2019quantitative} and the coarse Baum-Connes conjecture for spaces with \textit{finite decomposition complexity}.\\
\end{itemize}

Let us point out that hese results do not give new examples where the Baum-Connes conjecture, coarse or not, holds. All these coarse spaces are coarsely embeddable into Hilbert spaces and all these groups or groups actions are a-T-menable, which falls under the monumental results of \cite{HigsonKasparov}, \cite{TuThese} and \cite{Yu2}. Their interest lie in that these last papers are notoriously hard, and the controlled philosophy gives new proofs which follows the classical cutting and pasting technique.

\subsubsection*{Baum-Connes for groupoids with finite complexity}
  
\textit{with Rufus Willett, University of \Hawaii at M\={a}noa}\\

The notion of \textit{finite dynamical complexity} naturally generalizes to \'etale groupoids, and these should be natural candidates for which the Baum-Connes conjecture can be proven using controlled $K$-theory. In a recent preprint \cite{willett2019decompositions}, Rufus Willett defined \textit{local decomposabity} for $C^*$-algebras, inspired by the above decomposition properties. He is then able to derive a Mayer-Vietoris like sequence involving a $C^*$-algebra which decomposes in that sense over two of its subalgebras. If they are ideals, one recover the classical Mayer-Vietoris exact sequence. This is used to establish a stability result for the K\"unneth formula and a stability result for the vanishing of $K$-theory groups.

\begin{project}
Prove the Baum-Connes conjecture for groupoids with finite dynamical complexity by local decomposability techniques.  
\end{project} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{Getting rid of the $\varepsilon$ and $R$'s}

\textit{with Amine Marrakchi, Research Institute for Mathematical Sciences, Kyoto University}\\

The use of controlled $K$-theory is quite cumbersome. One has to keep track of $\varepsilon $ and $R$'s while doing already complicated $K$-theoretic computations. The following project is in the line of applying the controlled philosophy to $K$-theoretic computations, while trying to avoid keeping track of the propagation to every step. The idea is to define a global object in which appoximate relations become exact. \\

Let $A$ be a unital filtered $C^*$-algebra: $A$ is the closure of the union of a family  $\{A_r\}_{r>0}$ of closed self-adjoint subspaces such that $A_r A_s \subset A_{r+s}$. Define $\hat {l^\infty} (A)$ to be the closure in $\prod_{\N} A \otimes \mathfrak K$ of the union of 
\[\mathcal A_r = \prod_{i\in \N} A_r \otimes \mathfrak K \]
when $r>0$. Let $\omega\in \beta \N$ be a principal ultrafilter and define $\hat A_\omega$ to be the quotient of $\hat {l^\infty} (A)$ by the ideal 
\[ I_\omega = \{ (a_i) | \lim_\omega \|a_i \| = 0\}.\]
We call \textit{approximate ideal} of $A$ an ideal of $\hat A_\omega$. It can be shown that finite asymtotic dimension and finite dynamical complexity give rise to approximate ideals in $\hat{C^*(X)}_\omega$ and $\hat{C_r^*(G)}_\omega$ respectively. Moreover, in these cases, we have a genuine Mayer-Vietoris decomposition which, when evaluated at a finite place, gives back the quantitatve Mayer-Vietoris exact sequence. We thus can translate approximate ideals and quantitative relations into ideals and exact relations in the global algebra $\hat {l^\infty} (A)$.  

\begin{project}
Investigate stability properties of $K$-theoretic computations and the K\"unneth formula using $\hat {l^\infty} (A)$ and $\hat A_\omega$.
\end{project}  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Hilbert-Hadamard spaces and the Novikov conjecture}

%\textit{with Guoliang Yu, Texas A \& M University}\\ 


























