\documentclass[a4paper]{article}
\usepackage[frenchb,british]{babel}
%\usepackage[T1]{fontenc} 
\usepackage[utf8]{inputenc}      
\usepackage{url}                

\input{macro2}
%\geometry{hmargin=2.5cm,vmargin=1.5cm}

\title{Research statement}
% and PhD description}

\date{}
\author{ Cl\'ement Dell'Aiera}

\begin{document}
\maketitle

I received my PhD form the University of Lorraine in July 2017, under the supervision of Herv\'e Oyono-Oyono and Andrzej Zuk. I have been in a postdoctoral position at University of \Hawaii  at Manoa since August 2017, under the supervision of Rufus Willett. The website \url{http://math.hawaii.edu/~dellaiera/} contains all my preprints, and documents related to my research and teaching activities.\\ 

The rest of this document is devoted to a presentation of my research. I divided the piece into two parts: we first give an overview of \textit{Operator algebras} and \textit{Noncommutative Geometry} which is intended to be accessible to the non-specialist. I then move on to a more specific description of my work and projects. These are of course what I am focusing at the moment, and hopefully future encounters and experiences will broaden this list.

\section{General introduction}
\input{Intro}

\section{Accomplished work and future projects}
\input{Research}

\section{Organizational Activities}

While a graduate student at University of Lorraine, I co-organized the Graduate Seminar. This seminar was a place where graduate students could train at explaining their research and learn about other parts of Mathematics. Since I moved to University of \Hawaii, I have been co-organizing the Noncommutative Geometry Seminar, whose purpose is to educate graduate students, and introduce them to current trends in research via local and visiting speakers. In Fall 2019, I am co-organizing a week-long \href{http://math.hawaii.edu/~dellaiera/Conference.html}{conference} on $K$-theory and $C^*$-algebras in \Hawaii. \\

I maintain a webpage for the seminar:
\begin{center}
\url{https://clementstuff.wordpress.com/noncommutative-geometry/}
\end{center}
where, in addition to the schedule and abstracts, I regularly upload written notes that I take from the talks. \\

It happened that my students asked me questions during class, which I answered via blog entries on the same website (for instance one of the sections asked me for a list of books they could read during the summer in order to learn about science, the list is the first post).
 
\bibliography{biblio} 

\end{document}


























