
\begin{frame}{Künneth formula}
This result allows H. Oyono-Oyono and G. Yu to prove a permanence result (\cite{OY4}, Theorem $4.12$).
\begin{thmfr}
Let $A$ be a $\mathcal E$-filtered $C^*$-algebra. If for every $E\in \mathcal E$ there exists a $E$-controlled Mayer-Vietoris pair $(V_0, V_1, A^{(0)}, A^{(1)})$ such that $A^{(0)}$, $A^{(1)}$ and $A^{(0)} \cap A^{(1)}$ satisfy the quantitative Künneth formula then $A$ satisfies the quantitative Künneth formula.   
\end{thmfr}
\end{frame}

%%%%
%%%%%
\begin{frame}{Finite asymptotic nuclear dimension}
\begin{definitionfr}
A $\mathcal E$-filtered $C^*$-algebra $A$ is said to be locally bootstrap if, for every $E\in \mathcal E$, there exists $F\in \mathcal E$ and a sub-$C^*$-algebra $A^{(F)}$ of $A$, which is in the bootstrap class $\mathcal B$ and satisfies
\[A_E \subseteq A^{(F)}\subseteq A_F. \]
\end{definitionfr}
Remark: a locally bootstrap $C^*$-algebra is automatically bootstrap.\\
\end{frame}

\begin{frame}{Finite asymptotic nuclear dimension}
$\bullet$ $C_{fand}^{(0)}$: the class of locally bootstrap $C^*$-algebras. \\
$\bullet$ $C^{(n+1)}_{fand}$: $A$ which admits a Mayer-Vietoris pair in $C_{fand}^{(n)}$.\\
\[ C_{fand}  = \cup_{n\geq 0} C_{fand}^{(n)}.\]
 
\begin{thmfr}[\cite{OY4}]
Let $A$ be a filtered $C^*$-algebra with finite asymptotic nuclear dimension. Then $A$ satisfies the Künneth formula.\\ \end{thmfr}

\textbf{Applications:} \\
$\bullet$ The uniform Roe algebra of a coarse space with finite asymptotic dimension satisfies the Künneth formula \cite{OY4}.\\ 
$\bullet$ Stability of the Künneth formula for crossed products for groupoids. Do we have new examples?\\
\end{frame}

\begin{frame}{Stability for the Baum-Connes conjecture}
Guentner, Willett and Yu defined in \cite{GWY}:
\begin{itemize}
\item[$\bullet$] asymptotic dimension for \'etale groupoids,
\item[$\bullet$] finite decomposition complexity for group actions (FDC). 
\end{itemize}

\begin{thmfr}
For an action of a discrete group $\Gamma$ by homeomorphisms on a locally compact space $X$ with FDC, the assembly map
\[\mu_{\Gamma,X} : K^{top}(\Gamma,C_0(X))\rightarrow K_*(C_0(X)\rtimes_r \Gamma)\]
is an isomorphism.
\end{thmfr}

The proof uses the localization algebra, the equivalence of the assembly map with the evaluation at $0$ in $K$-theory, and quantitative $K$-theory (to show the vanishing of an obstruction group).
\end{frame}

\begin{frame}{Stability for the Baum-Connes conjecture}
Decompose \[G^{(0)} = U^0 \cup U^1, \]
such that $G_{(U_0)	_E}^{(E)}$ and $G_{(U_1)_E}^{(E)}$ belongs to some class $\mathcal C$.\\
\vspace{0.3in}
$\bullet$ Controlled assembly map $\mu_{G,A}: RK_*^G(P_E(G), A) \rightarrow \hat K_*(A\rtimes_r G)$,\\
\vspace{0.3in}
$\bullet$ Does the controlled assembly map commutes with the controlled Mayer -Vietoris boundary?\\ This would give an extension of the previous result, with a different proof.\\
Do we have a greater class that what was known before?
\end{frame}