\section{Quantitative products}

Let $\mathcal A=\{ A_i \}_{i\in I}$ be a family of $C^*$-algebras. We will denote by $l^\infty (\mathcal A)$ the $C^*$-algebra $\prod_{i\in I} A_i$. If the family is constant, $A_i=A$, we just write $l^\infty (A)$, and if not precised, $I $ is supposed to be countable. We denote by $c_0(\mathcal A)$ (resp. $c_0(A)$) the two-sided closed ideal $\bigoplus_I A_i$.\\

Let $A$ be a filtered $C^*$-algebra. The quantitative product $\hat l^\infty(A)$ is the sub-$C^*$-algebra of $l^\infty(A)$ given by the norm closure of  
\[ \cup_r \prod_{n\in \N} A_r. \]
We see $A$ as a subalgebra of $\hat l^\infty (A)$ by the constant embedding.\\

Let $\mathcal B =\{ B_n \}_{n\in \N}$ be a family of sub-$C^*$-algebras (operator spaces?) of $A$. The $r$-neighborhood of $B$ is defined as $N_r(B)=A_r B A_r$. Let $\hat l^\infty (\mathcal B)$ be the closure of
\[\cup_r \prod_{n\in\N} N_r(B_n) \cap A_r. \]
It is then easy to see that $\hat l^\infty (\mathcal B)$ is an ideal in $\hat l^\infty (A)$, even if it might not be proper. This construction will help building ideals out of \textit{approximate ideals}.\\

Let $X$ be a countable discrete coarse space with asymptotic dimension $1$. Pick a sequence $(r_n)$ of positive numbers that diverges to $+\infty$. For each $r_n>0$, let 
\[X = U_n \cup V_n\]
be a decomposition into two subspaces, each one being a $r_n$-disjoint union of uniformly bounded subspaces (of diameter less than $s_n$). Let $B_n$ (resp. $C_N$) be the algebra of bounded operators of $l^2 X$ supported on $U_n\times U_n$ (resp. $V_n\times V_n$). Denote by $I$ and $J$ the ideals $\hat l^\infty (\mathcal B)$ and $\hat l^\infty (\mathcal C)$ respectively. Then $I+J = ?$\\

Same thing for groupoids with dynamical asymptotic dimension $1$.\\

Let $A$ be a separable $C^*$-algebra with nuclear dimension $1$. \\

\subsection{The case of the integers}

Let $r_n$ be a sequence of positive numbers diverging to $+\infty$, and let 
\[U_n = \coprod_k [ 2k . 10 r_n  , (2k+1).10 r_n ] \quad \text{and}\quad V_n = \coprod_k [ (2k+1) . 10  r_n , (2k+2) . 10 r_n ],\]
so that $\Z = U_n \cup V_n$ for all $n$, and each part is a uniformly bounded $10r_n$-disjoint union of finite subsets.\\

We will be interested in the Roe algebra $A=C^*(\Z)$. Let  $B_n$ (resp. $C_n$) be the closure of the subspace of operators of finite propagation with support in $U_n \times U_n$ (resp. $V_n\times V_n$), and let $I$ (resp. $J$) the associated ideals in $\hat l^\infty (A)$.\\


