\documentclass[11pt]{article}

\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\hypersetup{                    % parametrage des hyperliens
    colorlinks=true,                % colorise les liens
    breaklinks=true,                % permet les retours à la ligne pour les liens trop longs
    urlcolor= blue,                 % couleur des hyperliens
    linkcolor= blue,                % couleur des liens internes aux documents (index, figures, tableaux, equations,...)
    citecolor= cyan               % couleur des liens vers les references bibliographiques
    }

\newcommand{\Manoa}{M\=anoa}
\newcommand{\Hawaii}{Hawai\kern.05em`\kern.05em\relax i}
\setlength{\parindent}{0 pt}
\textwidth=6.5truein
\textheight=8.5truein
\oddsidemargin=0.0truein
\evensidemargin=0.0truein
\topmargin=-0.25truein
\headheight=13pt
\headsep=0.3truein
\footskip=0.5truein
\parindent=18pt
\tolerance=6000
\parskip=0pt

\begin{document}

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

\section*{Biographical Sketch for PI Dell'Aiera}

\subsection*{Professional Preparation}

\begin{itemize}

\item[-] \emph{Undergraduate education:} 
\begin{itemize}
\item[$\bullet$] Classes pr\'eparatoires $MP^*$, Lyc\'ee Henri Poincar\'e, 2008-2011; 
\item[$\bullet$] Ecole Nationale de la Statistique et de l'Administration Economique (ENSAE Paristech), Data Science 2011;
\item[$\bullet$] Universit\'e Pierre et Marie Curie (Paris 6), Mathematics 2011-2012; 
\item[$\bullet$] ENS Rennes, Mathematics 2012-2014; 
\item[$\bullet$] Universit\'e Paris Diderot (Paris 7), Mathematics 2014;
\end{itemize}

\item[-] \emph{Graduate Education:} Universit\'e de Lorraine, Mathematics, Ph.D., 2017.


\item[-] \emph{Postdoctoral Institution:} University of \Hawaii~at \Manoa, Mathematics 2017-present.

\end{itemize}

\vspace{.5cm}

\subsection*{Appointments}

\begin{itemize}

\item[-]  Temporary Assistant Professor (non-tenure track), University of \Hawaii~at \Manoa,, 2017-present.\\

\end{itemize}

\vspace{.5cm} 

\subsection*{Products}

The following publications and preprints are particularly relevant to the current proposal. Preprints are available on my personal webpage \url{http://math.hawaii.edu/~dellaiera/Research.html}.

\begin{enumerate}
\item Cl\'ement Dell'Aiera, Controlled $K$-theory for groupoids and applications, PhD thesis, available at \url{https://math.hawaii.edu/~dellaiera/documentsE.html} .
\item Cl\'ement Dell'Aiera, Controlled $K$-theory for groupoids and applications to Coarse Geometry, Journal of Functional Analysis, Volume 275, Issue 7, October 2018, Pages 1756-1807
\item Cl\'ement Dell'Aiera, A K\"{u}nneth formula for \'etale groupoids in operator $K$-theory, Preprint 
\item Cl\'ement Dell'Aiera, Going-Down functors and the K\"unneth-formula for crossed products by ample groupoids (with Christian B\"onicke). In preparation, 2018. 
\end{enumerate}

\vspace{.5cm}

\subsection*{Synergistic activities}

\begin{itemize}
\item[-] Co-organizer, Noncommutative Geometry Seminar, University of \Hawaii, 2017-present.
\item[-] Member of the Colloquiium Committee, University of \Hawaii, 2017-present.
\item[-] Co-organizer of Young Researchers' Seminar, Universit\'e de Lorraine, 2016-2017.

\end{itemize}

\vspace{.2cm}

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%

\end{document}
