\documentclass[11pt]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace}
\RequirePackage{tikz, pgflibraryplotmarks}
\usepackage[margin=1in]{geometry}
\newcommand{\class}{Math 307	}
\newcommand{\term}{Fall 2018}
\newcommand{\examnum}{Final}
\newcommand{\examdate}{12/13/18}
\newcommand{\timelimit}{120 Minutes}
\singlespacing
\parindent 0ex

\begin{document}
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule
\begin{flushright}
\begin{tabular}{p{2.8in} r l}
\textbf{\class} & \textbf{Name (Print):} & \makebox[2in]{\hrulefill}\\
\textbf{\term} &&\\
\textbf{\examnum} &&\\
\textbf{\examdate} &&\\
\textbf{Time Limit: \timelimit} 
\end{tabular}\\
\end{flushright}
\rule[1ex]{\textwidth}{.1pt}

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{}{}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule

\begin{flushleft}
\begin{center}

\end{center}
\end{flushleft}

\hfill
\begin{minipage}[t]{4.3in}
\vspace{0pt}
%\cellwidth{3em}
\gradetablestretch{2}
\vqword{Problem}
\addpoints % required here by exam.cls, even though questions haven't started yet.	
\gradetable[v]%[pages]  % Use [pages] to have grading table by page instead of question

\end{minipage}


\pagebreak

\begin{questions}

\addpoints
\question[28]

Answer true or false to the following statements:
\vskip.2in
If $V$ is a vector space of dimension $n$, then $V$ is an $n \times n$ matrix.

\vfill
If $0$ is an eigenvalue of $A$, then $A$ is not invertible.   
\vfill
If $V$ is a vector space of dimension $n$, then any set of $n$ vectors must be linearly independent.

\vfill
If $\det(A) \neq 0$ then $A$ is invertible.
\vfill
If $A$ is an $n \times n$ invertible matrix, then the rows of $A$ are linerarly independent
\vfill
If $v_1$ and $v_2$ are linearly independent then there exists nonzero constants, $c_1$ and $c_2$, such that $c_1 v_1 +c_2 v_2 = 0$. 
\vfill
If $\lambda$ is an eigenvalue of $A$ then $\det(\lambda I - A)=0$. 
\vfill
If $V$ is a vector space of dimension $n$, then any collection of $n$ vectors forms a basis for $V$. 
\vfill
If $A$ is an $n \times n$ matrix with $n$ distinct eigenvalues, then $A$ is diagonalizable. 
\vfill
If $A$ is an $n \times n$ matrix with $n$ distinct eigenvalues, then $A$ is invertible. 

\vfill
If $A$ is an $n \times n$ matrix that is invertible, then $A$ is diagonalizable. 

\vfill
If $A$ is an $n \times n$ matrix that is diagonalizable, then $A$ is invertible. 
\vfill
If $V$ is a vector space of dimension $n$, then any basis has $n$ vectors.
\vfill
If $V$ is a vector space of dimension $n$, then any set of $n$ linearly independent vectors spans $V$.


\pagebreak

\addpoints
\question[15]

Consider the matrix 

$\begin{bmatrix}
1 & -1 & 1 \\
0 & 2 & 1 \\
0 & 0 & 2  \\
\end{bmatrix}$.
Determine the eigenvalues and associated eigenvectors.
\vfill
\vfill
What is the Jordan Normal Form of this matrix?
\vfill
\pagebreak

\addpoints
\question

Consider the homogeneous first order linear differential system
\begin{equation*}
  \begin{array}{l}
       x'=x-y+z\\
       y'=2y+z\\
       z'=2z\\
        \end{array}
    \end{equation*}
where $x,y,z$ are all functions of the variable $t$. 

\begin{parts}
\part[5] Write the system in the matrix form $Y'= AY$.
\vfill
\part[5] Is the matrix $A$ diagonalizable? (Hint: Problem 2)
\vfill
\part[5] Find the general solution to the homogeneous system $Y'= AY$. 
\vfill
\vfill
\vfill
\vfill

%(You will need to use the method of the integrating factor twice.)
\end{parts}

\pagebreak

\addpoints
\question[20]
Solve the initial value problem

$$
Y'=
\begin{bmatrix}
2 & 1 \\
1 & 2 
\end{bmatrix}
Y
+
\begin{bmatrix}
x \\
1
\end{bmatrix},
\quad \quad 
Y(0)=
\begin{bmatrix}
1 \\
1
\end{bmatrix}$$
There is space on the next page to continue your computation.

\newpage 
(Problem 4: Continued - below is space for computation)
\newpage

\addpoints
\question


Let's consider the non-homogeneous first order linear differential system
\begin{equation*}
\begin{array}{l}
       x'=x+y+z\\
       y'=y+z\\
       z'=y+z\\
        \end{array}
\end{equation*}
where $x,y,z$ are all functions of the variable $t$.

\begin{parts}
\part[5] Write the system in the matrix form $Y'= AY$.

\vfill
\vfill

\part [15] Find a diagonal matrix $D$ and an invertible matrix $P$ such that $P^{-1}AP=D$.


\vfill

\vfill

\vfill

\vfill

\vfill

\vfill

\vfill

\vfill

\pagebreak

 \part[5] Find the general solution to the homogeneous system $Z'=DZ$.

\vfill

 \part[5] Find the general solution to the homogeneous system $Y'=AY$.

\vfill

\vfill

\vfill

\vfill



\end{parts}

\newpage
\addpoints
\question
 Consider the following system:


\begin{align*}
{y_1}'' &= y_{1}'+y_{2}' + e^x \\
{y_2}'' &= y_1 + y_2 + \sin(x)
\end{align*}
where $y_1$ and $y_2$ are functions of $x$.
\begin{parts}
\part[5] Write this system as a system of first order liner differential equations.

\vfill

\part Extra Credit: Solve the system from part (a). 
\vfill
\pagebreak

\part[5] Write the following differential equation as a system of first order linear equations:

$$y''-y'-2y=0$$  

\vfill

\part[10] Solve the system from part b).

\vfill

\vfill

\vfill

\part[5] Verify your solution by solving the original differential equation by using it's characteristic polynomial.  
\vfill

\end{parts}


\newpage
\addpoints
\question[2]

Write an English sentence (without mathematical symbols) describing something interesting you learned in this class.

  

%$
%\begin{bmatrix}
 %   x_{11} & x_{12} & x_{13} & \dots  & x_{1n} \\
  %  x_{21} & x_{22} & x_{23} & \dots  & x_{2n} \\
   % \vdots & \vdots & \vdots & \ddots & \vdots \\
   % x_{d1} & x_{d2} & x_{d3} & \dots  & x_{dn}
%\end{bmatrix}
%$
\end{questions}
\end{document}
