\section{PhD description}

The starting point of my work was to use controlled K-theory for a restricted class of topological groupoids. Controlled K-theory is a refined version of operator K-theory for filtered $C^*$-algebras developed by Pr. H. Oyono-Oyono and Pr. Guoliang Yu in \cite{OY2}. Its motivation lies in a geometric approach for computing K-theory of $C^*$-algebras that was used in Yu’s celebrated  proof of the Novikov conjecture for finitely generated groups with finite asymptotic dimension in the sense of Gromov \cite{Yu1}. The idea is to extend this method to other $C^*$-algebras which contain geometric information, such as crossed-product algebras, algebras associated to foliations, or equivariant Roe algebras.\\

In a series of papers \cite{OY1}\cite{OY2}\cite{OY3}, Oyono-Oyono and Yu developed the theory for coarse spaces and their Roe algebras, and discrete groups and their crossed-product algebras. I followed their route, and extended this construction first to étale groupoids. I was then able to define a controlled assembly map \[\hat\mu_{A,G} : RK_*^G(P_E(G),B)\rightarrow \hat K_*(B\rtimes_r G)\] which factorizes the usual Baum-Connes assembly map in a precise way. This allows one to state very naturally a controlled version of the Baum-Connes conjecture for étale groupoids. One can define similarly a controlled Coarse Assembly map for any Coarse Space $X$, a construction detailed also in my thesis. It follows from the work of Pr. Georges Skandalis, Pr. Jean-Louis Tu and Pr. Guoliang Yu \cite{SkTuYu} that one can associate to a coarse space $X$ an ample groupoid $G(X)$ ( which is a special case of étale groupoid) and that the Coarse Assembly map for $X$ is equivalent in a precise way to the Baum-Connes assembly map for $G(X)$ with coefficients in $l^\infty(X,\mathfrak K)$. It turns out that this remains true at the level of the controlled version of these maps, which gives a nice connection between the coarse world and that of groupoids. \\

The factorization mentioned above gives several examples of groupoids satisfying the controlled conjecture. For example, if a coarse space admits a coarse fibered embedding, then Martin Finn-Sell showed \cite{FinnSellFibred} that the Coarse Baum-Connes conjecture holds for $X$. His proof uses the fact that some restriction of the coarse groupoid $G(X)$ is a-T-menable, and the equivalence of Skandalis, Tu and Yu. This is naturally generalized to controlled K-theory, thus refining a result of H. Oyono-Oyono and G. Yu \cite{OY3}: the controlled assembly map is a controlled isomorphism for coarse spaces admitting a fibered coarse embedding. Examples of spaces which are not coarsely embeddable into a Hilbert space but admits a fibered coarse embedding are easily constructed using expanders associated to a-T-menable discrete groups. Another class of examples satisfying the controlled Baum-Connes conjecture arise from crossed-product $C^*$-algebras of groups satisfying the Haagerup property. \\

Another part of my work was to study a controlled version of the Künneth formula for topological groupoids. We follow here the work of J. Chabert, S. Echterhoff and H. Oyono-Oyono \cite{ChabertEchtOy}, and define a  restriction principle for groupoids. We have to mention that Christian Bönicke developed first a restriction principle for ample groupoids, and that we benefited of several visits between Metz and Müenster to exchange ideas. Using this restriction principle for groupoids which satisfy a certain condition, we are able to prove that the controlled version of the Künneth formula holds for the reduced $C^*$-algebras of these groupoids. These nice groupoids include ample groupoids.\\

My last project is, following ideas from H. Oyono-Oyono and G. Yu, to study how to decompose groupoid so that their reduced $C^*$-algebras decompose according to what is called a controlled Mayer-Vietoris pair. The aim is to show how the decomposition transfers to $K$-homology, and to show that the controlled assembly map respects this decomposition in a precise way. This would give stability results for the controlled Baum-Connes conjecture that are not satisfied by the usual one. Hopefully, this should lead to a proof of the Baum-Connes conjecture for étale groupoids with finite dynamic asymptotic dimension in the sense of E. Guentner, R. Willett, and G. Yu \cite{GWY}.  This part is still work in progress, but we have done some progress during the last months.\\

