\section{Reminder of functional analysis}

The different topologies\\
Norm, weak-$*$.\\
Biduals\\

How to transform a metrically proper-action on a infinite dimensional Hilbert space into a proper action on a compact space using the weak-$*$ topology.

\section{Definitions}

Definiton of an abstract $C^*$-algebra as a $*$-algebra equipped with a $*$-norm which is complete.\\

Gelfand Naimark \\
GNS, proof. Shows that concrete and abstract $C^*$-algebras are the same. \\
Similarities between GNS and kernels representation thm\\
For this, need to define precisely the dual spaces of a $C^*$-algebras\\

KasparovStinepsring theorem\\


Examples!\\

How to build $C^*$-algebras
\begin{itemize}
\item unitalization(s), $A^+$ and $M(A)$.
\item generator and relations
\item sum
\item tensor products
\item completions of $*$-algebras. Morphism between different completions
\item crossed-products
\end{itemize}

\section{Exact sequences}

Exact sequences: in the case of completions of $*$-algebra, underline that it is a statement on the norms.\\

Commutative, Nuclear, Exact.\\

Ext(A,B) and BDF\\

\section{Roe algebras}

\section{Groupoid algebras}

Completions of $\C[G]$.

\section{Tensor products}

\section{Crossed products constructions}

Present the notion as a twisted tensor product. Then show different isomorphisms:
\[l^\infty(X)\rtimes_r G \cong C^*_u(X)\]
for $X=G $ or a box space $X_{\mathcal N}$. \\
Equivariant Roe algebra
\[C^*_G(X) \cong C_r^*(G)\otimes \mathfrak K(H_X)\]
for a proper cobounded action by isometries of $G$ on $X$.\\

Green's isomorphism 
\[\bigoplus_{s\in \Omega}(A\rtimes_r G_s) \otimes \mathfrak K(l^2X_s) \cong (C(X)\otimes A )\rtimes_r G\] 
\[Ind_F^G(A)\rtimes G \cong \left( A\otimes \mathfrak K(l^2 G)\right)^G\]

\section{Some theorems}
\begin{thm}
[Tu] If $G$ is a-T-menable then $C^*_r(G)$ is Bootstrap.
\end{thm}

\begin{thm}
If $G$ is a infinite hyperbolic group with property T, $C^*_r(G)$ is not $K$-nuclear.
\end{thm}

If $G$ is a-T-menable, the trivial and regular representations are homotopic. This cannot happen in the case of property T.\\

\subsection{Classification}

Some results without proofs.

\section{Problems}

Show that $\C \langle p,q \ : \ [p,q] = 1\rangle $ does not have a representation as bounded operators. Show there exists one such that one of them is bounded.\\

Classify the finite dimesional $C^*$-algebras using the GNS representations.\\

Classify the AF algebras.\\

Describe the $C^*$-algebra of a finite/compact group. Example: finite permutations groups, SU(2).
