\section{Definitions}

The plane\\
A surface\\
A riemanian manifold\\
Length spaces\\

Euclidean spaces, Hilbert spaces.\\
Infinite dimensional spaces, CAT(0) spaces, metric on probability measures.\\

Underline the difference between nice finite dimensional objects like a manifold or a Cayley graph and infinite dimensional functional spaces.\\

Interaction between metrics and topology.\\

Metrization theorem (A compact Hausdorff space is metrizable iff it is second countable)\\

The large scale geometry is not captured by the topology: $\sup \{ d(x,y) , 1\}$ generates the same topology but turns the space into a bounded one.

\section{Groups and their graphs}

Metric on a graph \\
Coarse union of graphs\\

Cayley graph\\
Box spaces

\section{Actions of groups}

Def.

\section{Compactifications}
 
Looking at infinity. Perspective and projective spaces. Compactifications. Trees, and Cantor subspaces. Hyperbolic spaces.
 
\subsection{Stone-\v{C}ech compactification}

\subsection{Limits spaces}

$X(\omega)$ \\

In the case of a group, a box space.
\[X(\omega) = |G| \]

\section{Infinite dimensional spaces}

Focus on Hilbert spaces. Equip the Hilbert space with the weak topology. The closed balls are then compact (Banach Alaoglu) Interesting applications?\\

Other interesting examples: spaces of probability measures, of repartition functions. Gauge fields theory = moduli space of connections on $G$-principal bundles.\\
A lot of metric on probablity measures are obtained as
\[d_{\mathcal F}(p,q) = \sup_{f\in \mathcal F} | \int f dp - \int f dq |\]
\begin{itemize}
\item $\mathcal F = \{f\in Lip \ : \  \| f\|_{Lip}\leq 1\}$ : Wasserstein,
\item $\mathcal F = \{\chi_B \ : \ B\in B(\mathbb R)\}$ : total variation,
\item $\mathcal F = \{\chi_{(-\infty , t]} \ : \ t\in \mathbb R \ \ : \ B\in B(\mathbb R)\}$ : Kolmogorov.
\end{itemize}
Banach algebras\\
Introduce concrete $C^*$-algebras as closed selfadjoint subalgebras of $B(H)$.\\

\section{Coarse embeddings into Hilbert spaces}

When does a metric space coarsely embeds into a Hilbert space? When the distance function gives a negative type kernel.\\

\subsection{Kernels}

Theory of kernels. Maybe RKHS and applications in statistics. Preparation for a-t-menability and equivariant coarse embedding. Setting: $G$ acts on $X$ metric, then $X$ CEH $G$-equivariantly iff there exists a $G$-invariant kernel. For $X= |G|$, we say a-T-menable. \\

f G is a-T-menable, then it admits a proper actions by affine isometries on a real Hilbert space.\\

Consequence: $\oplus_t GNS(\phi_t)$ representation always have almost invariant vectors and no invariant vectors when $G$ is infinite, so that property T prevents aTmenablity. Talk about the link between kernel and representations for groups, metric spaces and $*$-algebras.\\

\subsection{A-T-menablity and group actions}

What if a group is CEH? Then the exist $X$ compact metrizable such that $X\rtimes G$ is aTmenable. Moreover $X\times R_+$ endowed with the ``Skandalis'' topology is a model for $\underline E G $.

Examples\\

Expanders do not coarsely embed. Example: box spaces of property $\tau$ ((T) is enough). Example $SL(2,\Z)$ admits an expander box spaces. But does not have property (T) Problem?\\

\subsection{Tensor products of Banach spaces}

Talk a little bit about nuclearity.

\section{Problems}

Draw the Cayley graphs of $\Z$, $PSL(2,\Z)$, $\Z / (n) \ast \Z / (m)$ and Heisenberg.\\

Use a software to get the first Cayley graphs of $PSL(2,\Z_p)$.\\

Can two non isomorphic groups have isomorphic Cayley graphs? Yes, take two finite groups of same cardinality, and use the whole group minus the identity as a generating subset.\\

Show Milnor Svarc lemma.\\

\begin{thm}
Let $X$ be a proper geodesic metric space, and $G$ a group which acts on $X$ by isometries. If the action is proper and cocompact, then $G$ is finitely generated and the map
\[G \rightarrow X ; g\mapsto g\cdot x\]
is a quasi-isometry for any $x\in X$.
\end{thm}

Reproducing kernels.\\

Show that all metric spaces are embeddable into a Banach space. 
\[x\mapsto d(x, *), X\rightarrow l^\infty (X)\]

Let $f=\sum_n a_n z^n$ be an entire function with $a_n\leq 0$, and let $k: X\times X\rightarrow \R$ be a symmetric positive kernel. Describe the $GNS$-representation associated to $\sum_n a_n k(x,y)^n$ in terms of $GNS(k)$.

\section{References}

De la Harpe, Topics in GGT\\
Nowak, Yu, Large scale geometry\\
Parzen, Kernels\\
Roe, Lectures on Coarse Geometry\\
Spakula, Willett, Limits spaces\\
Roe, Index theory, coarse geometry and topology of manifolds\\
